\tw: a Xanalogical Storage and Authoring System

### 2003-02-15 papers/hypertext2003/paper.tex
More changes in response to Jim's comments.

Our system, though full-featured, was not designed to be ``the'' scalable xanalogical system that will carry us all into the future.
Instead, we focused on building a usable implementation of core xanalogical features for the purpose of experimentation.
Though scalability was not a design goal, \tw \  was built on top of technologies that have scaled well for other web-based projects \cite{Everything2, WikiWikiWeb, Wikipedia}.
Given these precedents, we believe that \tw \   could be scaled into a globally accessible system, albeit with minor code modifications and a sufficient hardware investment.

@@

Quotes can be extracted from documents and saved to a user's quote clipboard for later reference or use.
Figure \ref{fig:extractQuote} shows the interface for quote extraction. 
Quote references on a clipboard can be followed to see a quote's context.
The clipboard interface is shown in Figure \ref{fig:quoteClipboard}.
When creating a new document, a user can enter new text along with references to quotes from his or her quote clipboard, as seen in Figure \ref{fig:docCreate}.
A preview mode shows the new document with all quote references expanded, as seen in Figure \ref{fig:docPreview}.

@@

\begin{figure}[t]
\centering
\epsfig{file=images/quoteClipboard.eps, width=20pc}
\caption{The quote clipboard interface.}
\label{fig:quoteClipboard}
\end{figure}

@@

\tw \  provides no explicit document linking mechanism.
However, since quote context can be obtained easily, brief quotes can be used to emulate links between documents.
For an example of quotes used as links, see Figure \ref{fig:quotesAsLinks}.

\begin{figure}[t]
\centering
\epsfig{file=images/quotesAsLinks.eps, width=20pc}
\caption{Brief portions of documents can be quoted to emulate links.}
\label{fig:quotesAsLinks}
\end{figure}

@@

\subsubsection{Scalability Limitations}
The main scalability limitation of our implementation is the use of a filesystem as a data backend.
Each text chunk and document are stored in a separate file, and these data objects can be quite small.
A chunk file will be as large as the text it contains, but a document file stores only references.
For example, if a new document is created that references only one new chunk and contains no quotes, the document file will contain a single reference.
The example reference given above was represented using only 33 bytes of ASCII text.

@@

\bibliographystyle{abbrv}
\bibliography{paper}
\end{document}

>>>>

Our system, though full-featured, was not designed to be ``the'' scalable xanalogical system that will carry us all into the future.
Instead, we focused on building a usable implementation of core xanalogical features for the purpose of experimentation.
Though scalability was not a design goal, \tw \  was built on top of technologies that have scaled well for other web-based projects \cite{Everything2, WikiWikiWeb, Wikipedia}.
Given these precedents, our architecture could potentially be scalled to support large document collections.
Section \ref{sec:Scalability} discusses these scalability issues in more detail.

@@

Quotes can be extracted from documents and saved to a user's quote clipboard for later reference or use.
To extract a document region as a quote, the user inserts $<$\texttt{q}$>$ $<$$/$\texttt{q}$>$ tags around the desired region in a text area.
This interaction mechanism is arguably more elegant and less error-prone than mouse-based selection highlighting, especially when extracting large regions that span several screens full of text.
Figure \ref{fig:extractQuote} shows the interface for quote extraction. 
Each quote is assigned a $<$\texttt{q N}$>$ tag to be used when inserting the quote into new documents---$<$\texttt{q 3}$>$ refers to the quote at index three on the clipboard.
The use of these abreviated handles hides the complexity of references and document regions from the user.
After extracting a quote, the user never needs to deal directly with the document region again, though the original context of a quote can be seen with a single click from the quote clipboard.
The clipboard interface is shown in Figure \ref{fig:quoteClipboard}.
When creating a new document, a user can enter new text along with handle tags for quotes from his or her quote clipboard, as seen in Figure \ref{fig:docCreate}.
A preview mode shows the new document with all quote references expanded, as seen in Figure \ref{fig:docPreview}.

@@

\begin{figure}[t]
\centering
\epsfig{file=images/quoteClipboard.eps, width=20pc}
\caption{The quote clipboard interface.  Each quote is associated with a $<$\texttt{q N}$>$ reference tag, where \texttt{N} is the quote's index on the clipboard.}
\label{fig:quoteClipboard}
\end{figure}

Figures \ref{fig:extractQuote} through \ref{fig:docPreview} show a sequence of actions from a common usage scenareo:  extracting a quote, viewing the quote on the clipboard, creating a new document that uses the quote, and previewing the document.
After correcting the spelling mistake highlithed in Figure \ref{fig:docPreview}, the final step would be to submit the document.
Once submitted, the work becomes a full-fledged \tw \  document, making it readable and quotable by other users in the system.

@@

\tw \  provides no explicit document linking mechanism.
However, since quote context can be obtained easily, brief quotes can be used to emulate links between documents.
For example, to link to a target document called ``frequently asked questions,'' the title words of the document can be quoted.
When quote markers are shown in the linking document, the words ``frequently asked questions'' will be marked, and clicking on the words will lead to the context of the quote (in other words, to the target document ``frequently asked questions'').
If the title words are not appropriate for use as a link anchor, another more relevant phrase from the body of the target document can be quoted to form a link.
For an example of quotes used as links, see Figure \ref{fig:quotesAsLinks}.

\begin{figure}[t]
\centering
\epsfig{file=images/quotesAsLinks.eps, width=20pc}
\caption{Brief portions of documents can be quoted to emulate links.  Here, the titles of two documents, ``frequently asked questions'' and ``\tw \  history,'' have been quoted.}
\label{fig:quotesAsLinks}
\end{figure}

@@

\subsubsection{Scalability Limitations}
\label{sec:Scalability}
The main scalability limitation of our implementation is the use of a filesystem as a data backend.
Each text chunk and document are stored in a separate file, and these data objects can be quite small.
A chunk file will be as large as the text it contains, but a document file stores only references.
For example, if a new document is created that references only one new chunk and contains no quotes, the document file will contain a single reference.
The example reference given above was represented using only 33 bytes of ASCII text.

@@

\bibliographystyle{abbrv}
\bibliography{paper}

\end{document}
